%──────────────────────────────────────────────────────────────────────────────
% Benjamin Malemo – CV – Full-Stack Web & AI Developer
%──────────────────────────────────────────────────────────────────────────────
\documentclass[a4paper,9.5pt]{extarticle}

\usepackage[top=0.35in,bottom=0.25in,left=0.45in,right=0.45in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% ── Colours & links ───────────────────────────────────────────────────────────
\definecolor{heading}{HTML}{1A1A2E}
\definecolor{accentrule}{HTML}{16213E}
\definecolor{link}{HTML}{0F3460}
\hypersetup{colorlinks=true,urlcolor=link,pdfauthor={Benjamin Malemo},pdftitle={CV -- Benjamin Malemo}}

% ── Sections ──────────────────────────────────────────────────────────────────
% the rule color is pulled out of \uppercase scope to avoid the linter
% misreading "accent" as "ACCENT"
\newcommand{\sectionrule}{\textcolor{accentrule}{\rule{\linewidth}{0.7pt}}}
\titleformat{\section}{\normalsize\bfseries\color{heading}\uppercase}{}{0pt}{}[\vspace{-5pt}\sectionrule]
\titlespacing*{\section}{0pt}{6pt}{3pt}

% ── Lists ─────────────────────────────────────────────────────────────────────
\setlist[itemize]{leftmargin=12pt,itemsep=0.5pt,parsep=0pt,topsep=1pt,label=--}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ── Entry helper ──────────────────────────────────────────────────────────────
\newcommand{\entry}[3]{%
  \noindent\begin{minipage}{\linewidth}%
    \textbf{#1}\hfill\textit{\small #2}\\[-1pt]%
    \textit{\small #3}%
  \end{minipage}\vspace{1pt}%
}

\pagestyle{empty}

\begin{document}

% ═══════════════════════════════════════════════════════════════════════════════
% HEADER
% ═══════════════════════════════════════════════════════════════════════════════
\begin{center}
{\Large\bfseries\color{heading} BENJAMIN MALEMO}\\\vspace{2pt}
{\small Full-Stack Web \& AI Developer}\\\vspace{3pt}
{\small
+27\,83\,346\,8959\enspace|\enspace
\href{mailto:benjaminmalemo23@gmail.com}{benjaminmalemo23@gmail.com}\enspace|\enspace
\href{https://linkedin.com/in/benjamin-malemo-ai}{linkedin.com/in/benjamin-malemo-ai}\enspace|\enspace
\href{https://github.com/6enj1}{github.com/6enj1}\\[2pt]
\href{https://zenziai.africa}{zenziai.africa}\enspace|\enspace
Johannesburg, South Africa\enspace|\enspace
French / English / Swahili}
\end{center}
\vspace{-2pt}

% ═══════════════════════════════════════════════════════════════════════════════
% PROFILE
% ═══════════════════════════════════════════════════════════════════════════════
\section{Profile}
{\small Full-stack developer specialising in shipping end-to-end products across mobile and web. Founded \textbf{Kula} (kulasave.co.za) -- a food waste marketplace with a native iOS app (Swift/SwiftUI), a React 19 restaurant dashboard, and a production REST API -- and \textbf{ZenziAI}, a multimodal AI assistant platform for African SMEs (WhatsApp, web, voice). Comfortable across the full stack: SwiftUI, React/Next.js, Node/Express, PostgreSQL, AI integrations (GPT-4o, LangChain), and cloud deployment.}

% ═══════════════════════════════════════════════════════════════════════════════
% TECHNICAL SKILLS
% ═══════════════════════════════════════════════════════════════════════════════
\section{Technical Skills}
{\small
\begin{tabular}{@{}l@{\hskip 8pt}l@{}}
\textbf{Frontend:}      & TypeScript/JavaScript, React, Next.js, SwiftUI, Tailwind CSS, HTML/CSS \\
\textbf{Backend \& API:} & Node.js/Express, FastAPI, REST APIs, GraphQL, JWT/OTP, webhooks/IPN \\
\textbf{AI \& Voice:}    & OpenAI (GPT-4o), LangChain, ElevenLabs, Hugging Face, prompt engineering, RAG \\
\textbf{Data:}           & PostgreSQL, MongoDB, Supabase, Firebase, Prisma ORM, Redis \\
\textbf{DevOps:}         & Git/GitHub, Docker, GitHub Actions, Vercel, AWS (EC2/S3), Linux \\
\end{tabular}}

% ═══════════════════════════════════════════════════════════════════════════════
% PROJECTS
% ═══════════════════════════════════════════════════════════════════════════════
\section{Projects}

\entry{Kula -- Food Waste Marketplace (iOS, Web \& API)}{\href{https://www.kulasave.co.za}{kulasave.co.za}}{Founder \& Lead Developer \hfill Jan 2025 -- Present}
\begin{itemize}[nosep]
\item Shipped a full-featured \textbf{native iOS app} (Swift/SwiftUI, dark-mode glassmorphism UI) with on-device voice search (Speech API), CoreLocation restaurant discovery, QR-code order verification, Apple/Google OAuth, Keychain token storage, and Yoco checkout with 120-second payment polling.
\item Built a \textbf{restaurant web dashboard} (React 19, TypeScript, Vite, Zustand, React Query, Recharts, React Leaflet) with real-time order management (5-second polling, browser + audio notifications), bag CRUD with image upload, revenue analytics, and a 15\% commission model.
\item Engineered the production REST API at \texttt{api.kulasave.co.za} -- JWT auth with auto token refresh on 401, 20+ endpoints covering auth, bags, orders, analytics, and Yoco payments.
\item Launched \href{https://www.kulasave.co.za}{kulasave.co.za}: conversion-focused public site with restaurant earnings calculator, partner onboarding form, and legal pages, deployed via Vercel.
\end{itemize}

\vspace{2pt}
\entry{ZenziAI -- Multimodal AI Assistant for African SMEs}{\href{https://zenziai.africa}{zenziai.africa}}{Founder \& Full-Stack AI Developer \hfill Jan 2025 -- Present}
\begin{itemize}[nosep]
\item Launched a beta platform (WhatsApp, web dashboard, voice) on a Node/Express + PostgreSQL backend, integrating GPT-4o and ElevenLabs via \texttt{/api/chat} and \texttt{/api/voice} endpoints.
\item Implemented a full subscription system with Yoco (IPN, upgrades/downgrades) and automated PDF/CSV invoice generation.
\item Set up secure authentication (OTP + JWT) and admin-protected zones safeguarding client data.
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
% EXPERIENCE
% ═══════════════════════════════════════════════════════════════════════════════
\section{Experience}

\entry{Full Stack Web Development Intern}{\href{https://futureinterns.com}{Future Interns}}{Remote \hfill Jan 2026}
\begin{itemize}[nosep]
\item Completed a 1-month structured internship program with task-based full-stack assignments, applying frontend and backend concepts to practical deliverables.
\item Awarded Certificate of Completion (CIN: FIT/JAN26/FS10526) and a Letter of Recommendation for professionalism, technical problem-solving, and consistent delivery.
\end{itemize}

\vspace{2pt}
\entry{Freelance Web Developer}{Jun 2023 -- Present}{Johannesburg, South Africa}
\begin{itemize}[nosep]
\item Delivered responsive websites (portfolios, Shopify stores) end-to-end from design to deployment (Vercel/Netlify).
\item Integrated multilingual content (English/French/Swahili) with onboarding guides for client self-management.
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
% EDUCATION
% ═══════════════════════════════════════════════════════════════════════════════
\section{Education}

\entry{Diploma in Business Information Technology (NQF 6)}{Graduated 2025}{University of Johannesburg (UJ), Johannesburg, South Africa}
\begin{itemize}[nosep]
\item Coursework: Programming, Web Development, Databases (SQL), Systems \& Business Analysis, IT Security.
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
% CERTIFICATIONS
% ═══════════════════════════════════════════════════════════════════════════════
\section{Certifications}
{\small
\textbf{Full Stack Web Development -- Certificate of Completion} -- Future Interns, Jan 2026\enspace|\enspace
\textbf{IBM AI Developer Professional Certificate} -- Coursera, 2025\enspace|\enspace
\textbf{DeepLearning.AI ``AI for Everyone''} -- Coursera, 2025
}

% ═══════════════════════════════════════════════════════════════════════════════
% INVOLVEMENT & INTERESTS
% ═══════════════════════════════════════════════════════════════════════════════
\section{Involvement \& Interests}
{\small
\textbf{Volunteering:} Source of Life Church -- Children's ministry leader (2023 -- present).\enspace
\textbf{Languages:} French (fluent), English (fluent), Swahili (fluent).\enspace
\textbf{Interests:} AI for Africa, food sustainability, tech entrepreneurship.
}

\end{document}
